Using reference models in variable selection \vspace{.1in}

### 2022-01-18 reviews/rebuttal.tex

	\vspace{0.5cm}

\end{reply}

\begin{point}
Please include the computational cost of compared approaches in Section 2.1. 
\end{point}

\begin{reply}
Thanks for the suggestion. We discuss the computational aspects in Section 2.2. In general, the reference model approach has the additional cost of fitting the reference model before performing selection. However, this reference models is usually available anyway when building up a model via robust workflows \citep{gelman2020bayesian}. Therefore, in these cases there is no additional cost. In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
\fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
\end{reply}

@@

\begin{point}
Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
\end{point}

\begin{reply}
This is a good idea. We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:

\vspace{0.5cm}
\textit{
``The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.''
}
\vspace{0.5cm}
\end{reply}

### 2022-01-18 paper/ref_approach.tex
computational time for bodyfat example

If one of the models to be compared is the full model, which can be
used as a reference model, there is no additional cost of using a
reference model as it was estimated as part of the analysis anyway.
Sometimes including all the available variables in an
elaborate model can be computationally demanding.  In such a
case, even simpler screening or dimensionality reduction techniques,
as for example the supervised principal components
\citep{bair2006prediction,piironen2018} can produce useful reference
models.

>>>>

If one of the models to be compared is the full model, which can be
used as a reference model, there is no additional cost of using a
reference model as it was estimated as part of the analysis anyway.
Sometimes including all the available variables in an
elaborate model can be computationally demanding.  In such a
case, even simpler screening or dimensionality reduction techniques,
as for example the supervised principal components
\citep{bair2006prediction,piironen2018} can produce useful reference
models. \fede{As an example, Table \ref{tab:computational_time} reports
the computational time for the body fat data example of Section \ref{bodyfat-1}. 
For reference model approaches, i.e. projpred and ref+step.lm, the main
time consuming operation is to fit the reference model. The burden of it depends clearly
on the specific application and type of model used.}

\begin{table}[tp]
	\footnotesize
	\centering
	\begin{tabular}{l|cc|ccc}
		Data & Reference model & Search path & projpred & step.lm & ref + step.lm \\
		\hline
		body fat & 37.661 & 15.289 & 52.95 &  &  \\
		  &  & 0.078 &  & 0.078 &  \\
		  & 37.661 & 0.078 &  &  & 37.739 \\
		\hline 
		+ noisy variables & 169.797 & 77.638 & 247.435 &  &  \\
		  & & 12.019 & & 12.019 & \\
		  & 169.797 & 12.019 & & & 181.816

	\end{tabular}
	\caption{Computational time (in seconds) of body fat example of Section \ref{bodyfat-1}.
		The reported time is the sum of the time to fit the reference model (second column) and
		to explore the search path (third column), according to the method.}
	\label{tab:computational_time}
\end{table}
